Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-03-18 paper.tex
remove comma
fix reference

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.

@@

\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Schönknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

>>>>

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health with serious consequences.

@@

\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.
